### 2015-10-27 ch02-qlogms/logMS_IMTC.tex
emove old bib defs

\def\thisDir{ch02-qlogms}
\TODO{reshape figures}
\TODO{rename labels}
\TODO{import specific bib items}
% \begin{abstract}
% The logarithmic distribution of spectral lines in excitation signals is widely used to measure the transfer functions of dynamic systems over a wide frequency band, covering several decades.
% Periodic signals are very popular in many advanced dynamic signal analyzers.
% Generating multitone periodic signals requires an equidistant frequency grid which conflicts with the logarithmic distribution, especially at the low frequencies.
% In this paper we offer an elegant solution to get around this problem using an improved choice for the amplitude spectrum of the multitone.
% We also offer a simple way to tune the frequency spacing of such a signal to allow for robust identification of the system under test.
% \end{abstract}

\section{Introduction} \label{sec:intro}
  It often occurs that we wish to measure the frequency response function (FRF) of a linear time invariant (LTI) system in a frequency band that covers several decades \citep{bragos2001characterisation,sanchez2011optimal,niedostatkiewicz2009,VanGheem2004}.
  Of course, we also want to attain a specified uncertainty level over the full frequency span.

>>>>

\TODO{reshape figures}
\TODO{rename labels}
\TODO{import specific bib items}
% \begin{abstract}
% The logarithmic distribution of spectral lines in excitation signals is widely used to measure the transfer functions of dynamic systems over a wide frequency band, covering several decades.
% Periodic signals are very popular in many advanced dynamic signal analyzers.
% Generating multitone periodic signals requires an equidistant frequency grid which conflicts with the logarithmic distribution, especially at the low frequencies.
% In this paper we offer an elegant solution to get around this problem using an improved choice for the amplitude spectrum of the multitone.
% We also offer a simple way to tune the frequency spacing of such a signal to allow for robust identification of the system under test.
% \end{abstract}

\section{Introduction} \label{sec:intro}
  It often occurs that we wish to measure the frequency response function (FRF) of a linear time invariant (LTI) system in a frequency band that covers several decades~\citep{Bragos2001,Sanchez2011,Niedostatkiewicz2009,VanGheem2004}.
  Of course, we also want to attain a specified uncertainty level over the full frequency span.
